Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 4.dev

### 2025-11-30 main.tex
Added descriptions to the parameters table in the appendix.

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters for the balance assist bicycle with and without a rider.
These are found using the measurement approach for geometric and inertial
parameters for a bicycle explained in \cite{Moore2012}. The rider inertial
parameters are derived from the 83.5~\si{\kilogram} rider ``Jason'' available
in BicycleParameters~1.1.1~\cite{Moore2024}. The variable names match the
notation and definitions from the benchmark bicycle model presented
in~\cite{Meijaard2007}.
%
\begin{table}[ht]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{llrr}
    \toprule
    Variable & Unit & Without Rider & With Rider \\
    \midrule
    \(c\) & \si{\meter} & 0.04 & 0.04 \\
    \(g\) & \si{\meter\per\second\squared} & 9.80665 & 9.80665 \\
    \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 19.7 \\
    \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & -3.5 \\
    \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 22.7 \\
    \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 5.0 \\
    \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0995 \\
    \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.1902 \\
    \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.298 \\
    \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & -0.038 \\
    \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.257 \\
    \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.057 \\
    \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.1023 \\
    \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.1887 \\
    \(\lambda\) & \si{\radian} & 0.25 & 0.25 \\
    \(m_B\) & \si{\kilogram} & 22.50 & 106.00 \\
    \(m_F\) & \si{\kilogram} & 2.23 & 2.23 \\
    \(m_H\) & \si{\kilogram} & 4.30 & 4.30 \\
    \(m_R\) & \si{\kilogram} & 4.08 & 4.08 \\
    \(r_F\) & \si{\meter} & 0.3523 & 0.3523 \\
    \(r_R\) & \si{\meter} & 0.3489 & 0.3489 \\
    \(w\) & \si{\meter} & 1.113 & 1.113 \\
    \(x_B\) & \si{\meter} & 0.52 & 0.374 \\
    \(x_H\) & \si{\meter} & 0.92 & 0.92 \\
    \(z_B\) & \si{\meter} & -0.52 & -1.009 \\
    \(z_H\) & \si{\meter} & -0.860 & -0.860 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters for the balance assist bicycle with and without a rider.
These are found using the measurement approach for geometric and inertial
parameters for a bicycle explained in \cite{Moore2012}. The rider inertial
parameters are derived from the 83.5~\si{\kilogram} rider ``Jason'' available
in BicycleParameters~1.1.1~\cite{Moore2024}. The variable names match the
notation and definitions from the benchmark bicycle model presented
in~\cite{Meijaard2007} with the \(xyz\) axes following the SAE J670 standard
with positive \(z\) directed down into the ground.
%
\begin{table}[ht]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{lllrr}
    \toprule
    Description & Variable & Unit & Without Rider & With Rider \\
    \midrule
    trail & \(c\) & \si{\meter} & 0.04 & 0.04 \\
    acceleration due to gravity & \(g\) & \si{\meter\per\second\squared} & 9.80665 & 9.80665 \\
    rear frame moment of inertia & \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 19.7 \\
    rear frame product of inertia & \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & -3.5 \\
    rear frame moment of inertia & \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 22.7 \\
    rear frame product of inertia & \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 5.0 \\
    front wheel moment of inertia & \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0995 \\
    front wheel moment of inertia & \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.1902 \\
    front frame moment of inertia & \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.298 \\
    front frame product of inertia & \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & -0.038 \\
    front frame moment of inertia & \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.257 \\
    front frame moment of inertia & \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.057 \\
    rear wheel moment of inertia & \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.1023 \\
    rear wheel moment of inertia & \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.1887 \\
    steer axis tilt & \(\lambda\) & \si{\radian} & 0.25 & 0.25 \\
    rear frame mass & \(m_B\) & \si{\kilogram} & 22.50 & 106.00 \\
    front wheel mass & \(m_F\) & \si{\kilogram} & 2.23 & 2.23 \\
    front frame mass & \(m_H\) & \si{\kilogram} & 4.30 & 4.30 \\
    rear wheel mass & \(m_R\) & \si{\kilogram} & 4.08 & 4.08 \\
    front wheel radius & \(r_F\) & \si{\meter} & 0.3523 & 0.3523 \\
    rear wheel radius & \(r_R\) & \si{\meter} & 0.3489 & 0.3489 \\
    wheelbase & \(w\) & \si{\meter} & 1.113 & 1.113 \\
    rear frame mass center coordinate & \(x_B\) & \si{\meter} & 0.52 & 0.374 \\
    front frame mass center coordinate & \(x_H\) & \si{\meter} & 0.92 & 0.92 \\
    rear frame mass center coordinate & \(z_B\) & \si{\meter} & -0.52 & -1.009 \\
    front frame mass center coordinate & \(z_H\) & \si{\meter} & -0.860 & -0.860 \\
    \bottomrule
  \end{tabular}
\end{table}
